\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation of timber volume resources on forest district levels \\ \vspace{2ex} \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}

### 2017-12-18 Draft_Form/tex/Results.tex
Initial commit 18_12_2017
Initital commit

\section{Methods}
\label{sec:Meth}

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %

\subsection{Terrestrial Sampling Design of the German NFI}
\label{sec:germanNFI}

The German National Forest Inventory (German NFI) is a periodic inventory that is carried out every 10 years over the entire forest area of Germany. The most recent inventory (BWI3) was conducted in the years 2011 and 2012. While information was originally gathered at a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid. The German NFI uses a cluster sampling design, which means that a sample unit consists of maximal four sample locations (also referred to as \textit{sample plots}) that are arranged in a square (so called \textit{cluster}) with a side length of 150 metres (Picture). The number of plots per cluster can however vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}. In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}, using a basal area factor ($BAF$) of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the tree-individual inclusion circle \citep{bwi3_aufn}. A further inventory threshold for a tree to be recorded is a diameter at breast height ($dbh$) of at least 7 cm. For each sample tree that is selected by this procedure, the dbh, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to calculate a volume estimation on the tree level. These volume estimations are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Estimators}
\label{sec:estimators}

% ++++++++++++ %
\subsubsection{Double Sampling in the Infinite Population Approach}
\label{sec:inf_pop}

% \subsubsection{One- and Two-Phase Sampling in the Infinite Population Approach}

The estimators used in this study have been proposed by \citep{mandallaz2013a,mandallaz2013b} and build upon the so called infinite population approach (IPA) in order to bridge the inventory procedure and the derived information to the mathematics behind the estimators. Therefore, we shall first provide a short introduction into this general estimation frame. We start by assuming that the population $P$ of trees $i \in 1,2, ..., N$ within a forest of interest $F$ is exactly defined, and each tree $i$ has a directly or indirectly observable response variable $Y_i$ (e.g. its timber volume) that allows to specify the population mean $Y$ (e.g., the average timber volume per unit area) over $F$. If a full census of all tree population individuals is not possible, $Y$ has to be estimated by the conduction of an inventory.  The infinite population approach assumes that the spatial distribution of the local density $Y(x)$ (e.g., the timber volume per unit area) at each point or location $x$ in the forest $F$ is given by a fixed (i.e. non stochastic) piecewise constant function. The population mean $Y$ is thus mathematically equivalent to the integral of the density function surface divided by the forest area $\lambda(F)$, i.e. $Y=\frac{1}{\lambda(F)} \sum_{i=1}^{N}Y_i=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$, and thus the population mean $Y$ corresponds to a spatial mean. Since the local density function is in practice always unknown, one estimates $Y$ by collecting a sample $s_2$ of all local density values by the conduction of a terrestrial inventory at $n_2$ uniformly and independently distributed sample points over $F$. This procedure is often referred to as \textit{one-phase sampling} (OPS). Opposed to the one-phase approach, \textit{two-phase} or \textit{double-sampling} procedures use information from two nested samples (phases). Practically speaking, the terrestrial inventory $s_2$ is embedded in a large phase $s_1$ comprising $n_1$ sample locations that each provide a set of explanatory variables described by the column vector $\pmb{Z}(x)=(z(x)_1, z(x)_2,...,z(x)_p)^{\top}$ at each point $x \in s_1$. These explanatory variables are derived from auxiliary information that is available in high quantity within the forest $F$. For every $x \in s_1$, $\pmb{Z}(x)$ is transformed into a prediction $\hat{Y}(x)$ of $Y(x)$ using the choice of some prediction model. The basic idea of this method is to boost the sample size by providing a large sample of less precise but cheaper predictions of $Y(x)$ in $s_1$ and to correct any possible model bias, i.e., $\EX{(Y(x)-\hat{Y}(x))}$, using the subsample of terrestrial inventory units where the value of $Y(x)$ is observed.

% which in \pkg{forestinventory} is always a linear model fit in $s_2$ using ordinary least squares (OLS).
%The one-phase and two-phase estimators applied in this study have been implemented in the software-package \textit{forestinventory} \cite{forestinventory} 
% The local density $Y(x)$ is in practice derived by ...
% extend the approach to collecting auxiliary information ...
% say that we also assume that the forest area is well-defined ...

% ++++++++++++ %
\subsubsection{SRS Estimator for Cluster Sampling}
\label{sec:srs_estimator}

The simple random sampling (SRS) estimator for cluster sampling was applied under the existing one-phase sampling design of the German NFI in order to obtain a point and variance estimate for the mean timber volume in each small area unit (Section \ref{sec:studyarea}). In order to provide all estimators in the infinite population framework and ensure a consistent terminology with the two-phase estimators in Section \ref{sec:SAestimators}, we will introduce the SRS estimator in the form given in \citet{mandallaz2008, mandallaz2016}. In order to calculate the local density $Y_{c}(x)$ at the cluster level, a cluster is defined as consisting of $M$ sample locations (in the BWI3, we have $M=4$ ) where $M-1$ sample locations $x_2, ..., x_M$ are created close to the cluster origin $x_1$ by adding a fixed set of spatial vectors $e_2, ..., e_M$ to $x_1$. The actual number of plots per cluster, $M(x)$, is a random variable due to the uniform distribution of $x_l$ ($l=1, ..., M$) in the forest $F$ and forest/non-forest decision for each sample location $x_l$:

\begin{equation}\label{eq:Mx}
M(x)=\sum_{l=1}^{M}I_{F}(x_l) \hspace{3ex} \text{where} \hspace{3ex} I_F(x_l)=\begin{cases}&1 \text{ if $x_l \in F$}\\
&0 \text{ if $x_l\not\in F$}
\end{cases}
\end{equation}

The local density on cluster level $Y_{c}(x)$, in our case the timber volume per hectare, is then defined as the average of the individual sample plot densities $Y(x_l)$:

\begin{equation}\label{eq:locdens_clust}
Y_{c}(x) = \frac{\sum_{l=1}^{M} I_{F}(x_{l}) Y(x_l)}{M(x)}
\end{equation}

The local density $Y(x_l)$ on individual sample plot level was calculated according to the description in \citet{mandallaz2008}, which can be rewritten for angle-count sampling technique applied in the BWI3. The general form of $Y(x)$ in \citet{mandallaz2008} is given as the Horwitz-Thompson estimator

%\begin{equation}\label{locdens_plot}
%Y(x)= \sum_{i=1}^{F}\frac{I_{i}(x)Y_i}{\varPi_{i}\lambda(F)} = \sum_{i \in s_{2}(x)}\frac{Y_i}{\varPi_{i}\lambda(F)}
%\end{equation}

\begin{equation}\label{eq:locdens_plot}
Y(x_l)=\sum_{i \in s_{2}(x_l)}\frac{Y_i}{\pi_{i}\lambda(F)}
\end{equation}

where $Y_i$ is in our case the predicted timber volume of the tree $i$ recorded at sample location $x$ in m$^3$. Each tree has an inclusion probability $\pi_{i}$ that is well defined as the proportion of its inclusion circle area $\lambda(K_i)$ within the forest area $\lambda(F)$, i.e. via their geometric intersection:

%with the binary indicator variable $Ii$ for the $i$th tree defined as
%
%\begin{equation}\label{1stage}
%I_i(x)=\begin{cases}&1 \text{ if $x \in K_i$}\\
%&0 \text{ if $x\not\in K_i$}
%\end{cases}
%\end{equation}

\begin{equation}\label{locdens_plot_1}
\pi_{i} = \frac{\lambda(K_i \cap F)}{\lambda(F)}
\end{equation}

The radius $R_i$ of the tree-individual inclusion circle $K_i$ is given by $R_i = bhd_{i}/cf_{i,corr}$ (also referred to as \textit{limiting distance}), where $cf_{i,corr}$ is the counting factor corrected for potential boundary effects at the forest border. In case of angle-count sampling, we can rewrite $\pi_{i}$ as

\begin{equation}\label{eq:locdens_plot_2}
\pi_{i} = \frac{G_i}{cf_{i,corr}\lambda(F)}
	\end{equation}

since the intersection area $\lambda(K_i \cap F)/\lambda(F)$ can be expressed using the trees basal area $G_i$ (in m$^2$) and the corrected counting factor:

\begin{equation}\label{eq:locdens_plot_3}
\lambda(K_i \cap F) = \frac{G_i}{cf_{i, corr}} \hspace{3ex} \text{where} \hspace{3ex} cf_{i,corr} = cf\frac{\lambda(K_i)}{\lambda(K_i \cap F)}
\end{equation}

Using Eq. \ref{eq:locdens_plot_2} in Eq. \ref{eq:locdens_plot} yields the rewritten form of $Y(x_l)$ for angle count sampling that conforms to the definition used in the BWI3 algorithms \citep{bwi3_ausw}:

\begin{equation}\label{eq:locdens_plot_4}
Y(x_l)= \sum_{i \in s_{2}(x_l)} \frac{cf_{i, corr}Y_i}{G_i} = \sum_{i \in s_{2}(x_l)} nha_{i}{Y_i}
\end{equation}

where $nha_i$ is the number of trees per hectare represented by tree $i$. The local densities on cluster level can then be used to derive the estimated spatial mean $\hat{Y}_c$ and its estimated variance $\hat{\var}(\hat{Y}_c)$ for any given spatial unit for which $n_2 \geq 2$ ($n_2$ denoting the number of sample units, i.e. clusters):

\begin{subequations}\label{eq:srs_est_cluster}
	\begin{align}
\hat{Y}_c &= \frac{\sum_{x \in s_2} M(x) Y_{c}(x)}{\sum_{x \in s_2} M(x)} \\
\hat{\var}(\hat{Y}_c) &= \frac{1}{n_2(n_2 - 1)}\sum_{x \in s_2}\Big(\frac{M(x)}{\bar{M_2}}\Big)^2(Y_{c}(x) - \hat{Y}_c)^2
	\end{align}
\end{subequations}

\newpage

% +++++++++++++++++++++++++++++ %
\subsubsection{Design-Based Small Area Regression Estimators for Cluster Sampling}
\label{sec:SAestimators}

All three considered small area estimators have in common that they use ordinary least square (OLS) regression models to produce the predictions of the local density $Y_{c}(x)$ directly on the cluster level $c$. We consider the \textit{internal model approach}, where the vector of estimated regression coefficients on the cluster level is found by "borrowing strength" from the entire terrestrial sample $s_2$ of the current inventory:

\begin{subequations}\label{normequ_simple_cluster}
	\begin{align}
\hat{\pmb{\beta}}_{c,s_2} &= \pmb{A}_{c,s_2}^{-1} \Big(\frac{1}{n_2}\sum_{x\in{s_2}}M(x)Y_{c}(x)\pmb{Z}_{c}(x)\Big) \\
\pmb{A}_{c,s_2} &=\frac{1}{n_2}\sum_{x\in{s_2}}M(x)\pmb{Z}_{c}(x)\pmb{Z}_{c}^{\top}(x)
	\end{align}
\end{subequations}

\noindent $\pmb{Z}_{c}(x)$ is the vector of explanatory variables on the cluster level, which is calculated as the weighted average of the explanatory variables $\pmb{Z}(x_l)$ on the individual plot levels $x_1, ..., x_l$ (Eq.\ref{eq:Zc(x)}). The weight $w(x_l)$ is the proportion of the support-area within the forest $F$ used to derive the explanatory variables from the raw auxiliary information.

\begin{equation}\label{eq:Zc(x)}
\pmb{Z}_{c}(x)=\frac{\sum_{l=1}^{M}I_{F}(x_l)w(x_l)\pmb{Z}(x_l)}{\sum_{l=1}^{M}I_{F}(x_l)w(x_l)}
\end{equation}

\noindent The estimated design-based variance-covariance matrix $\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}$ accounts for the fact that the regression model is internal by reflecting the dependency of the estimated regression coefficients on the realized sample $s_2$. It is defined as

\begin{equation}\label{eq:varcovarbeta}
\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{s_2}}=\pmb{A}_{c,s_2}^{-1}
\Big(\frac{1}{n_2^2}\sum_{x\in{s_2}}M^{2}(x)\hat{R}_{c}^2(x)\pmb{Z}_{c}(x)\pmb{Z}_{c}^{\top}(x)\Big)
\pmb{A}_{c,s_2}^{-1}
\end{equation}

\noindent with $\hat{R}_{c}=Y_{c}(x)-\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2}$ being the empirical model residuals at the cluster level, which by construction of OLS satisfy the important \textit{zero mean residual property}, i.e. $\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)}=0$.\\

 In the following, we will give a short description of each small area estimator and refer to \citet{mandallaz2013a, mandallaz2016, mandallaz2013b} if the reader requires additional details or proofs. The estimators have also been implemented in the R-package \textit{forestinventory} \citep{forestinventory} which was used to compute all estimates in this study.\\

% ----------------------------- %
% PSMALL estimator:
\textbf{Pseudo Small Area Estimator (\psmall{})}\\

All point information used for small area estimation is now restricted to that available at the sample locations $s_{1,G}$ or $s_{2,G}$ in the small area $G$, with exception of $\hat{\pmb{\beta}}_{c,s_2}$ and $\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}$ which are always based on the entire sample $s_2$. We thus first define the following quantities on the small area level:

\begin{subequations}\label{eq:compsG}
	\begin{align}
	\hat{\bar{\pmb{Z}}}_{c,G} &= \frac{\sum_{x \in s_{1,G}} M_{G}(x) \pmb{Z}_{c,G}(x)}{\sum_{x \in s_{1,G}} M_{G}(x)} \label{eq:meanZcG} \hspace{3ex} &\text{where} \hspace{3ex}
	\pmb{Z}_{c,G}(x) =  \frac{\sum_{l=1}^{L} I_{G}(x_l)\pmb{Z}(x_l)}{M_{G}(x)}\\		
	Y_{c,G}(x) &= \frac{\sum_{l=1}^{L} I_{G}(x_l)\pmb{Y}(x_l)}{M_{G}(x)}  &\text{and} \hspace{3ex}
	\hat{Y}_{c,G}(x)=\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2}\\
	\bar{\hat{R}}_{2,G} &= \frac{\sum_{x \in s_{2,G}} M_{G}(x) \hat{R}_{c,G}(x)}{\sum_{x \in s_{2,G}} M_{G}(x)} \hspace{3ex} &\text{where} \hspace{3ex}
	\hat{R}_{c,G}(x) = Y_{c,G}(x)-\hat{Y}_{c,G}(x)
	\end{align}
\end{subequations}

Note that the restriction to $G$, i.e. $I_{G}(x_l)=\{0,1\}$, is made on the individual sample plot level $x_l$, and $M_{G}(x) = \sum_{l=1}^{L}I_{G}(x_l)$ thus is the number of sample plots per cluster within the small area. The asymptotically design-unbiased point estimate of \textit{PSMALL} is then defined according to Eq. \ref{eq:psmall_pest}. The first term estimates the small area population mean of $G$ by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$. The second term then corrects for a potential bias of the regression model predictions in the small area $G$ by adding the mean of the empirical residuals $\bar{\hat{R}}_{2,G}$ in $G$. This correction insures that the \textit{zero mean residual property} in $F$ also holds within the small area $G$, which is per se not ensured by fitting the regression coefficients with data outside $G$.

\begin{subequations}\label{eq:psmall}
	\begin{align}
	\hat{Y}_{c,G,PSMALL} &= \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2} + \bar{\hat{R}}_{2,G} \label{eq:psmall_pest} \\
	\hat{\var}(\hat{Y}_{c,G,PSMALL}) & = \hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}\hat{\bar{\pmb{Z}}}_{c,G}
	+ \hat{\pmb{\beta}}_{c,s_2}^{\top}\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}\hat{\pmb{\beta}}_{c,s_2} \nonumber \\
	& + \frac{1}{n_{2,G}(n_{2,G}-1)}\sum_{x \in s_{2,G}}\Big(\frac{M_{G}(x)}{\bar{M}_{2,G}}\Big)^2(\hat{R}_{c,G}(x) - \bar{\hat{R}}_{2,G})^2
	\label{eq:psmall_var}
	\end{align}
\end{subequations}

The estimated design-based variance of $ \hat{Y}_{c,G,PSMALL}$ is given by Eq. \ref{eq:psmall_var}. Basically, the first term constitutes the variance introduced by the uncertainty in the regression coefficients, whereas the second term expresses the variance caused by estimating the exact auxiliary mean using the sample $s_{1,G}$. The third term is the variance of the model residuals and thus accounts for the inaccuracies of the model predictions. Note that the first term can also be rewritten using g-weights \cite[pg.14]{mandallaz2016} which ensure calibration properties of the auxiliary variables on the terrestrial sample.\\

The variance-covariance matrix of the auxiliary vector $\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}$ is thereby defined as

\begin{equation}\label{estvarcovaux_G}
\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}} = \frac{1}{n_{1,G}(n_{1,G}-1)} \sum_{i \in s_{1,G}} \big(\frac{M_{G}(x)}{\bar{M}_{1,G}}\big)^2 (\pmb{Z}_{c,G}(x)-\hat{\bar{\pmb{Z}}}_{c,G})(\pmb{Z}_{c,G}(x)-\hat{\bar{\pmb{Z}}}_{c,G})^{\top}
\end{equation}

with $\bar{M}_{1,G}=\frac{\sum_{i \in s_{1,G}}M_{G}(x)}{n_{1,G}}$.\\

% ----------------------------- %
% PSYNTH estimator:
\newpage
\textbf{Pseudo Synthetic Estimator (\psynth{})}\\

The \psynth{} estimator is commonly applied when no terrestrial sample is available within the small area $G$ (i.e. $n_{2,G}=0$). The point estimate (Eq. \ref{eq:psynth_pest}) is thus only based on the predictions generated by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$. Note that the bias correction term using the empirical residuals (Eq. \ref{eq:psmall_pest}) can no longer be applied. The \psynth{} estimator thus has a potential unobservable design-based bias.

\begin{subequations}\label{eq:psynth}
	\begin{align}
	\hat{Y}_{c,G,PSYNTH} & =\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\beta}}_{c,s_2} \label{eq:psynth_pest} \\
	\hat{\var}(\hat{Y}_{c,G,PSYNTH})& =
	\hat{\bar{\pmb{Z}}}_{c,G}^{\top}\hat{\pmb{\Sigma}}_{\hat{\pmb{\beta}}_{c,s_2}}
	\hat{\bar{\pmb{Z}}}_{c,G}
	+ \hat{\pmb{\beta}}^{\top}_{c,s_2}\hat{\Sigma}_{\hat{\bar{\pmb{Z}}}_{c,G}}\hat{\pmb{\beta}}_{c,s_2} \label{eq:psynth_var}
	\end{align}
\end{subequations}

The uncertainty of the model predictions can also no longer be considered in the variance estimation (Eq. \ref{eq:psynth_var}). The synthetic estimator will therefore usually have a smaller variance than estimators incorporating the model uncertainties, but at the cost of a potential bias. Note that the \psynth{} estimator is still design-based, but one purely has to rely on the validity of the regression model within the small area as it is the case in the model-dependent framework.\\

% ----------------------------- %
% EXTPSYNTH estimator:
\textbf{Extended Pseudo Synthetic Estimator (\extpsynth{})}\\

The \extpsynth{} estimator (Eq. \ref{eq:extpsynth}) has been proposed by \cite{mandallaz2013a} as a transformed version of the \psmall{} estimator that has the form of the \psynth{} estimator but remains asymptotically design unbiased. It has the advantage that the mean of the empirical model residuals of the regression model for the entire area $F$ and the small area $G$ are by construction both zero at the same time, i.e. $\bar{\hat{R}}_{c} = \bar{\hat{R}}_{c,G} = 0$. This is realized by \textit{extending} the auxiliary vector $\pmb{Z}_{c}(x)$ by the indicator variable $I_{c,G}$ which takes the value 1 if the entire cluster lies within the small area $G$ and 0 if the entire cluster is outside $G$, i.e. $I_{c,G}(x)=\frac{M_{G}(x)}{M(x)}$. The extended auxiliary vector thus becomes $\pmb{\mathbb{Z}}_{c}^{\top}(x)= (\pmb{Z}_{c}^{\top}(x),I_{c,G}(x))$ and the new regression coefficient using $\pmb{\mathbb{Z}}_{c}(x)$ instead of $\pmb{Z}_{c}(x)$ in Eq. \ref{normequ_simple_cluster} is denoted as $\hat{\pmb{\theta}}_{s_2}$. All remaining components are calculated by plugging in $\pmb{\mathbb{Z}}_{c}(x)$ in Eq. \ref{eq:compsG}. A decomposition of $\hat{\pmb{\theta}}_{s_2}$ reveals that the residual correction term is now included in the regression coefficient $\hat{\pmb{\theta}}_{s_2}$.

\begin{subequations}\label{eq:extpsynth}
	\begin{align}
	\hat{Y}_{c,G,EXTPSYNTH} & =\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}^{\top}\hat{\pmb{\theta}}_{c,s_2} \label{eq:extpsynth_pest} \\
	\hat{\var}(\hat{Y}_{c,G,EXTPSYNTH})& =
	\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}^{\top}\hat{\pmb{\Sigma}}_{\hat{\pmb{\theta}}_{c,s_2}}
	\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}
	+ \hat{\pmb{\theta}}^{\top}_{c,s_2}\hat{\pmb{\Sigma}}_{\hat{\bar{\pmb{\mathbb{Z}}}}_{c,G}}\hat{\pmb{\theta}}_{c,s_2} \label{eq:extpsynth_var}
	\end{align}
\end{subequations}

However, it is important to note that $\bar{\hat{R}}_{c,G} = 0$ under the extended regression model only holds if the sample plots $x_1, ..., x_l$ of a cluster are \textit{all} either inside our outside the small area, i.e. $M_G(x)\equiv M(x)$, and thus $I_{c,G}(x)=\frac{M_{G}(x)}{M(x)}$ can only take the values 1 or 0. \citet{mandallaz2016} assumed that the effects on the estimates should be negligible as the number of occasions where $M_{G}(x) < M(x)$ was considered to be small in practical implementations. It was thus a further objective of this study to investigate the actual occurrences and effects of this phenomenon by comparing the estimates of \extpsynth{} to those of \psmall{}. % where the estimates stay unaffected

\subsubsection{Measures of Estimation Accuracy}

The estimation accuracies were quantified by the \textit{estimation error}, which is the ratio of the standard error and the point estimate:

\begin{equation}\label{eq:error}
error(\hat{Y})_{[\%]}=\frac{\sqrt{\var(\hat{Y})}}{\hat{Y}}*100
\end{equation}

We further calculated the 95\% confidence interval for each estimate for visualization purpose. The confidence intervals can also be used for hypothesis testing whether the point estimates of the three estimators for a given small area are statistically different. The confidence intervals under SRS can be obtained as:

\begin{equation}\label{ci_1phase}
CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
\hat{Y}+t_{n_{2}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
\end{equation}

The confidence intervals for the \psmall{} and \extpsynth{} estimates are calculated as:

\begin{equation}\label{ci_2phase_sae}
CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
\hat{Y}+t_{n_{2,G}-1, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
\end{equation}

For the \psynth{} estimates, the confidence intervals are

\begin{equation}\label{ci_2phase_global}
CI_{1-\alpha}(\hat{Y})=\bigg{\lbrack}\hat{Y}-t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})},
\hat{Y}+t_{n_{2}-p, 1-\frac{\alpha}{2}}\sqrt{\hat{\var}(\hat{Y})}\bigg{\rbrack}
\end{equation}

In order to address the potential benefits of the small area estimators compared with the SRS approach, we calculated the \textit{relative efficiency} (Eq. \ref{eq:releff}) which can be interpreted as the relative sample size under SRS needed to achieve the variance under the double sampling estimators.

\begin{equation}\label{eq:releff}
rel.eff_{[\%]}=\frac{\hat{\var}_{SRS}(\hat{Y})}{\hat{\var}_{SAE_{2phase}}(\hat{Y})}\cdot100
\end{equation}

\newpage

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\section{Materials}
\label{sec:Mat}

%This section describes the actual implementation of the proposed small area estimators (Section \ref{sec:estimators}) under the cluster design of the German NFI (Section \ref{sec:germanNFI}) in the federal state Rhineland-Palatinate.

\subsection{Study Area and Small Area Units}
\label{sec:studyarea}

The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium (figure \ref{fig:Study Area}). With 42.3\% (appr. 8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}. The forests of RLP are further characterized by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterized by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a. Hunsr{\"u}ck and Palatinate forest) up to mixed forests comprising variable proportions of oak, larch, spruce, Scots pine and beech. Around 82\% of the forest area in RLP are mixed forest stands and 69\% of the forest area exhibit a multi-layered vertical structure. The forest area of RLP are divided into 3 ownership classes, i.e. state forest (27\%), communal forest (46\%) and privately owned forest (27\%). The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}. For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (figure xx). On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 426 Forstreviere (\textit{FR}). The next level are the actual forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5- to 10 year period in order to set up management strategies for the upcoming 10 years. The FAs and FRs constituted the small area (SA) units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}. The average area of the SA units were 43'777 ha on the FA-level, and 4624 ha on the FR level.\\

% | managment level | average area (min-max)  | average no cluster (plots) | min no. cluster (plots | max no. cluster (plots |
%   FA                43'777 ha  (17367 - 125423)     46 (128)         11 (36)            64 (198)
%   FR                4624 ha   (0.68 - 43284)         5  (14)          0 (0)             13 (34)
%   stand level       6 ha     (0.03 ha - 73)          0 (0)            0 (0)             2 (4)

% Add Graphic 1:
% - Graphic of RLP with "zoom" in the 3 managament units (or later all together in Graphic

% Add in text:
% - add information on the (average) spatial area of each sae-level

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Extension to Double Sampling Design}

Rhineland-Palatinate (RLP) is covered by a 2x2 km inventory grid of the German NFI, where timber volume information was derived for 2810 cluster (8092 plots) in the field survey of the latest inventory. The local timber volume density on the plot and cluster level for this sample was consequently calculated according to Section \ref{sec:srs_estimator}. In the frame of the last inventory (BWI3), the plot center coordinates have been re-measured with differential global satellite navigation system (DGPS) technique. Knowledge about the exact plot positions were considered crucial to provide optimal comparability between the terrestrially observations and the information derived from the auxiliary information. A comparison of the DGPS coordinates with the so-far used target coordinates revealed that 90\% of all horizontal deviations lay in the range of 25 meters. A detailed analysis of horizontal DGPS errors in RLP by \citet{lambrecht2017} indicated that 80\% of the plots should not exceed horizontal DGPS errors of 8 meters. For 162 plots, the DGPS coordinates were replaced by their target coordinates due to missingness or implausible values.\par

In order to apply the small area estimators (Section (\ref{sec:SAestimators}), the existing NFI design was extended to a double sampling design by densifying the existing systematic 2x2 km grid to a 500x500 m sample grid that constituted the large first phase $s_1$ in accordance to Section \ref{sec:inf_pop} (Figure xx). The existing terrestrial phase $s_2$ was consequently integrated by replacing the target coordinates of the respective $s_1$ cluster by the terrestrially measured DGPS coordinates. For our study, we restricted the \textit{sampling frame} to the communal and state forest. The forest/non-forest decision for each plot was thereby made by a spatial intersection of the plot center coordinates with a polygon layer of the communal and state forest stands provided by the forest service. The terrestrial sample size was thus reduced to 2055 cluster (5791 plots). Using this stand layer provided the advantage to consistently apply the same forest/non-forest definition to the entire sample $s_1$ in order to decide about excluding or including a plot in the sampling frame.\par

\begin{figure}[H]
	\centering
	\resizebox{0.75\hsize}{!}{\includegraphics*{fig/SAunitsRLP.png}}
	\caption{Forest management units in Rhineland-Palatinate, overlayed with the extended double sampling cluster design.}
	\label{fig:StudyArea}
\end{figure}

% NOTES:
%
% Add Table:
% provide table of "forest characteristics" in RLP
% adress sample sizes before and after extension (table?)
%
% move this to discussion:
% It should however be mentioned that a discrepancy between the terrestrially made forest/non-forest decision and that based on the polygon stand layer can lead to missing responses in the terrestrial sample $s_2$. This occurs if a terrestrial plot $x_l \in s_2$ does not provide the terrestrial response variable although its plot center would theoretically fall within the boundaries of the stand layer. For these cases, it is important to note that according to the double sampling estimator described in Section \ref{sec:SAestimators}, the plots of a cluster can either only belong to the sample $s_2$ or $s_1$. The missing terrestrial plot information $Y(x)$ can thus not be replaced by a prediction $\hat{Y}(x)$, i.e. by establishing a plot $x \in s_1$ instead, and has thus to be treated as a non-response.\par
%
%  "This extension led to a considerable increase of the sample size $n_{1,G}$ in the small area units of both, the FA and FR level."
% - Show (theoretical) increase in sample sizes by extension to 2phase scheme 
%   --> these sample sizes are in the following reduced by missing rs-info
%
% - Add Graphik showing RLP, zoom into 3 management levels including 2-phase sample
%   (big graphic, can take 1/2 page later)

% ----------------------------------------------------------------------- %
% Table xx provides an overview of the terrestrial sample sizes on these management levels for the state and communal forest areas.

% \input{terrSamplsizeFoaFuWa.tex}

% average no. plots / clusters; average area of all three units (divided by state + communal forest & entire forest area)

% --> this is only for communal & state forest area:
% | managment level | average area (min-max)  | average no cluster (plots) | min no. cluster (plots | max no. cluster (plots |
%   FA                43'777 ha  (17367 - 125423)     46 (128)         11 (36)            64 (198)
%   FR                4624 ha   (0.68 - 43284)         5  (14)          0 (0)             13 (34)
%   stand level       6 ha     (0.03 ha - 73)          0 (0)            0 (0)             2 (4)

% - Verwaltungsebenen: management levels (Forstamt, Revier, Bestände) -> durschnittliche Flächengrössen (für die sollen die sae schätzungen gemacht werden)
% - evtl bereits Stichprobenzahlen generell und innerhalb der Managementenheiten nennen (das ginge dirket hinsichltich des eigentlichen Themas)
%   (das generelle Problem der Stichprobenanzahl in diesen Einheiten wurde ja schon in der Einleitung angesprochen, also könnte man
%    hier direkt ein Beispiel geben) --> hier noch getrennt nach gesamter Wald und nur Woefis-Wald (Tabelle, Grpahik)
% - warum RLP ? (neues Informationssystem, Interesse an effizienteren Methoden)
% wir nennen Fortamt einfach 'FA-level' und Forstrevier einfach 'FR-level' :-)
% Info: 45 Forstämter without Bundesforstamt; 426 Reviere without Bundesforstamt
% mention that the boundaries of all these management units are well-defined by polygon masks (that were used to extract the sampling
% frame)
% ----------------------------------------------------------------------- %

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Auxiliary Information}
\label{sec:auxinfo}

% ! Mention Missingness in the data and resulting reduction of the sample size (s1, s2)

% ----------------------------------------- %
\subsubsection{LiDAR Canopy Height Model}
\label{sec:chm}

>>>>

\section{Results} %techreport
\label{sec:Res}

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
%\subsection{Model Validations}
%\label{sec:modval_res}
